---
title: "Brms_growth_height_Gompertz_4p"
output: html_notebook
---
<br>

**Go to (the end of this file) for the parameter estimates of the best fitted model on phenotype height** 

<br>

Trying to fit non-linear model with BRMS(Bayesian Regression Models using Stan)
<br>
```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(magrittr)
library(ggforce)
library(gtable)
library(reshape2)
library(brms)
library(loo)
library(mice)
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
options(max.print=999999)
library(reshape2)
library(DMwR)
```

```{r, message=FALSE}
heights <- read_csv("heights.csv")
heights

sample.list <- unique(heights$ID)
```
<br><br>  
    
      
### Plant height phenotype
<br>

166 individuals at 4 time points

```{r}
ggplot(data=heights, aes(x=days, y=height, group=ID)) +
    geom_line(alpha=.1) + 
    geom_point(size=.1, alpha=.05) +
    ggtitle("height by days") 
```


```{r include=FALSE}
# for fixing the bug of facet_wrap_paginate()
facet_wrap_paginate <- function(facets, nrow = NULL, ncol = NULL, scales = "fixed",
                                shrink = TRUE, labeller = "label_value", as.table = TRUE,
                                switch = NULL, drop = TRUE, dir = "h", strip.position = 'top', page = 1) {
  facet <- facet_wrap(facets, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, labeller = labeller, as.table = as.table,
                      switch = switch, drop = drop, dir = dir,
                      strip.position = strip.position)
  if (is.null(nrow) || is.null(ncol)) {
    facet
  } else {
    ggproto(NULL, FacetWrapPaginate, shrink = shrink,
            params = c(facet$params, list(page = page)))
  }
}

FacetWrapPaginate <- ggproto("FacetWrapPaginate", FacetWrap,
                             setup_params = function(data, params) {
                               modifyList(
                                 params,
                                 list(
                                   max_rows = params$nrow,
                                   nrow = NULL
                                 )
                               )
                             },
                             compute_layout = function(data, params) {
                               layout <- FacetWrap$compute_layout(data, params)
                               layout$page <- ceiling(layout$ROW / params$max_rows)
                               layout
                             },
                             draw_panels = function(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params) {
                               include <- which(layout$page == params$page)
                               panels <- panels[include]
                               ranges <- ranges[include]
                               layout <- layout[include, , drop = FALSE]
                               layout$ROW <- layout$ROW - min(layout$ROW) + 1
                               x_scale_ind <- unique(layout$SCALE_X)
                               x_scales <- x_scales[x_scale_ind]
                               layout$SCALE_X <- match(layout$SCALE_X, x_scale_ind)
                               y_scale_ind <- unique(layout$SCALE_Y)
                               y_scales <- y_scales[y_scale_ind]
                               layout$SCALE_Y <- match(layout$SCALE_Y, y_scale_ind)
                               table <- FacetWrap$draw_panels(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params)
                               if (max(layout$ROW) != params$max_rows) {
                                 spacing <- theme$panel.spacing.y %||% theme$panel.spacing
                                 missing_rows <- params$max_rows - max(layout$ROW)
                                 strip_rows <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$l %in% panel_cols(table)$l])
                                 strip_rows <- strip_rows[as.numeric(table$heights[strip_rows]) != 0]
                                 axis_b_rows <- unique(table$layout$t[grepl('axis-b', table$layout$name)])
                                 axis_b_rows <- axis_b_rows[as.numeric(table$heights[axis_b_rows]) != 0]
                                 axis_t_rows <- unique(table$layout$t[grepl('axis-t', table$layout$name)])
                                 axis_t_rows <- axis_t_rows[as.numeric(table$heights[axis_t_rows]) != 0]
                                 table <- gtable_add_rows(table, unit(missing_rows, 'null'))
                                 table <- gtable_add_rows(table, spacing * missing_rows)
                                 if (length(strip_rows) != 0) {
                                   table <- gtable_add_rows(table, min(table$heights[strip_rows]) * missing_rows)
                                 }
                                 if (params$free$x) {
                                   if (length(axis_b_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_b_rows]) * missing_rows)
                                   }
                                   if (length(axis_t_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_t_rows]) * missing_rows)
                                   }
                                 }
                               }
                               if (max(layout$COL) != params$ncol) {
                                 spacing <- theme$panel.spacing.x %||% theme$panel.spacing
                                 missing_cols <- params$ncol - max(layout$COL)
                                 strip_cols <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$t %in% panel_rows(table)$t])
                                 strip_cols <- strip_cols[as.numeric(table$widths[strip_cols]) != 0]
                                 axis_l_cols <- unique(table$layout$l[grepl('axis-l', table$layout$name)])
                                 axis_l_cols <- axis_l_cols[as.numeric(table$widths[axis_l_cols]) != 0]
                                 axis_r_cols <- unique(table$layout$l[grepl('axis-r', table$layout$name)])
                                 axis_r_cols <- axis_r_cols[as.numeric(table$widths[axis_r_cols]) != 0]
                                 table <- gtable_add_cols(table, unit(missing_cols, 'null'))
                                 table <- gtable_add_cols(table, spacing * missing_cols)
                                 if (length(strip_cols) != 0) {
                                   table <- gtable_add_cols(table, min(table$widths[strip_cols]) * missing_cols)
                                 }
                                 if (params$free$y) {
                                   if (length(axis_l_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_l_cols]) * missing_cols)
                                   }
                                   if (length(axis_r_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_r_cols]) * missing_cols)
                                   }
                                 }
                               }
                               table
                             }
)

n_pages <- function(plot) {
  page <- ggplot_build(plot)$layout$panel_layout$page
  if (!is.null(page)) {
    max(page)
  } else {
    NULL
  }
}
```

plot by ID
```{r results='hide', fig.keep='all'}
lapply(1:6, function(i) {
    ggplot(heights) +
      geom_line(aes(x=days, y=height, group=ID)) +
      facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
    }
)
```

<br>

#### Try Gomertz (4-parameter) (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS

First set up the formula
```{r}
gompertz_4p.bf1 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-k*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

    Hmax, asymptotic height at which growth is zero
    Hmin, lower asymptotic height
    k, growth rate
    I, time at the inflection point

```{r}
stat.data <- function(fn) {
  fn %>% 
  group_by(days) %>%
  summarize(meadian=median(height),
            max=max(height),
            min=min(height),
            sd=sd(height))
}

stat.data(heights)
```

Priors.  Hmin and Hmax use median at start and end dates.
```{r results='hide'}
prior1 <- c(prior(normal(170,10), nlpar="Hmax"), 
            prior(normal(15,5), nlpar="Hmin"),
            prior(normal(.5,1), nlpar="k"), 
            prior(normal(160,10), nlpar="I"))

fit1 <- brm(formula=gompertz_4p.bf1,
            data=heights,
            prior=prior1)
```

```{r}
summary(fit1, waic=TRUE, R2=TRUE)
```

```{r results='hide',fig.keep='all'}
plot(fit1)
pairs(fit1)
```

```{r results='hide'}
prior2 <- c(prior(normal(170,10), nlpar="Hmax"), 
            prior(normal(15,5), nlpar="Hmin"),
            prior(normal(.5,1), nlpar="k", lb=0), 
            prior(normal(160,10),nlpar="I"))

fit2 <- brm(formula=gompertz_4p.bf1,
            data=heights,
            prior=prior2)
```

```{r}
summary(fit2, waic=TRUE, R2=TRUE)
```

```{r results='hide',fig.keep='all'}
plot(fit2)
pairs(fit2)
```

<br>
rescale k to get it more reasonable

```{r}
gompertz_4p.bf2 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

```{r results='hide'}
prior3 <- c(prior(normal(170,10), nlpar="Hmax"), 
            prior(normal(15,5), nlpar="Hmin"),
            prior(normal(.5,1), nlpar="k", lb=0), 
            prior(normal(160,10),nlpar="I"),
            prior(cauchy(0,1), class="sigma"))

fit3 <- brm(formula=gompertz_4p.bf2,
             data=heights,
             prior=prior3)
```

```{r}
summary(fit3, waic=TRUE, R2=TRUE)
```

```{r results='hide',fig.keep='all'}
plot(fit3)
pairs(fit3)
```

<br>
What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(heights$days), max(heights$days),1))
fit3.fitted <-  cbind(newdata, fitted(fit3, newdata)) %>% as.tibble() %>%
  rename(height=Estimate, lower.ci=`2.5%ile`, upper.ci=`97.5%ile`)
```

plot
```{r results='hide', fig.keep='all'}
ggplot(aes(x=days,y=height), data=heights) + 
  geom_line(aes(group=ID), alpha=.1) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.fitted)
```
<br>
**Now try adding random effects for model parameters:**

What parameters do we think might be interesting to allow to vary?  Probably not Hmin.  Try making a series of plots to see how varying delta or k affects things:

```{r results='hide',fig.keep='all'}
gompertz_4p.fn <- function (Hmax, Hmin, k, I, days) {
    Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))) 
}

for(k1 in seq(0,1,.2)) {
  tmp.heights <- gompertz_4p.fn(Hmax=172,
                                Hmin=15,
                                k=k1,
                                I=149,
                                days=newdata$days)
  abc <- data.frame(newdata$days, tmp.heights)
  p <- ggplot(data=abc, aes(newdata$days, tmp.heights)) +
    geom_line() + ylim(0,250) + ggtitle("k=",k1)
  print(p)
}
```


First try with only fixing Hmin

```{r}
gompertz_4p.bf3 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))), 
  Hmax + k + I ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```

```{r results='hide'}
prior4 <- c(prior(normal(170,10), nlpar="Hmax"), 
            prior(normal(15,5), nlpar="Hmin"),
            prior(normal(.5,1), nlpar="k", lb=0), 
            prior(normal(160,10),nlpar="I"),
            prior(cauchy(0,1), class="sigma"),
            prior(cauchy(0,10), class=sd, nlpar="Hmax"),
            prior(cauchy(0,10), class=sd, nlpar="I"),
            prior(cauchy(0,1), class=sd, nlpar="k"))

fit5 <- brm(formula=gompertz_4p.bf3,
            data=heights,
            prior=prior4,
            iter=5000)
```


```{r}
summary(fit5, waic=TRUE, R2=TRUE)
```

get fitted values
```{r}
b <- heights %>% ungroup()
fit5.fitted <- cbind(b, fitted(fit5)) %>% as.tibble()
fit5.fitted
```

plot 
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.fitted)
```

plot fitted vs actual
```{r results='hide', fig.keep='all'}
plot.fitted.actual <- function(fn) {
  
  r_squared <- summary(lm(Estimate ~ height, data=fn))$adj.r.squared
  r_squared <- round(r_squared, digits=4)

  fn %>%
    mutate(days=as.factor(days)) %>%
    ggplot(aes(x=height, y=Estimate, shape=days, color=days)) +
    geom_point() +
    geom_abline(intercept = 0, slope=1) +
    ggtitle(paste0("R2 = ",r_squared))
}
```

```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.fitted)
```

SSR
```{r}
total_sum_of_squared_residuals <- function(fn) {anova(lm(Estimate ~ height, data=fn))[2,2]}
```

cv
```{r results='hide', message=FALSE}
SSR.fit <- total_sum_of_squared_residuals(fit5.fitted)
waic.fit <- round(waic(fit5)$waic, digits=2)
kfoldic.fit <- round(kfold(fit5)$kfoldic, digits=2)
```

<br>

### 2) heights.mean

```{r, message=FALSE}
heights.mean <- read_csv("heights.mean.csv")
heights.mean
```

```{r results='hide', fig.keep='all'}
 lapply(1:6, function(i) {
       ggplot(aes(x=days, group=ID), data=heights.mean) +
         geom_line(aes(y=height), color="red") +   #red: modified data
         geom_line(aes(y=height_raw), color="black") +
          facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
}
)
```


#### Try Gomertz (4-parameter) (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS

First set up the formula
```{r}
gompertz_4p.bf1 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-k*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

```{r}
stat.data(heights.mean)
stat.data(heights)
```

```{r}
gompertz_4p.bf2 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #paramters do not vary for individuals
  nl=TRUE)
```

```{r results='hide'}
prior3.mean <- c(prior(normal(170,10), nlpar="Hmax"), 
                 prior(normal(15,5), nlpar="Hmin"),
                 prior(normal(.5,1), nlpar="k", lb=0), 
                 prior(normal(160,10),nlpar="I"),
                 prior(cauchy(0,1), class="sigma"))

fit3.mean <- brm(formula=gompertz_4p.bf2,
             data=heights.mean,
             prior=prior3.mean)
```

```{r}
summary(fit3.mean, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean)
pairs(fit3.mean)
```

<br>
What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(heights.mean$days), max(heights.mean$days),1))
fit3.mean.fitted <-  cbind(newdata, fitted(fit3.mean, newdata)) %>% as.tibble() %>%
  rename(height=Estimate, lower.ci=`2.5%ile`, upper.ci=`97.5%ile`)
```

plot
```{r results='hide', fig.keep='all'}
ggplot(aes(x=days,y=height), data=heights.mean) + 
  geom_line(aes(group=ID), alpha=.1) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.fitted)
```

<br>
**Now try adding random effects for model parameters:**

try with only fixing Hmin

```{r}
gompertz_4p.bf3 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))),  
  Hmax + k + I ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean <- c(prior(normal(170,10), nlpar="Hmax"), 
                 prior(normal(15,5), nlpar="Hmin"),
                 prior(normal(.5,1), nlpar="k", lb=0), 
                 prior(normal(160,10),nlpar="I"),
                 prior(cauchy(0,1), class="sigma"),
                 prior(cauchy(0,10), class=sd, nlpar="Hmax"),
                 prior(cauchy(0,10), class=sd, nlpar="I"),
                 prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean <- brm(formula=gompertz_4p.bf3,
                 data=heights.mean,
                 prior=prior4.mean,
                 iter=5000)
```

```{r}
summary(fit5.mean, waic=TRUE, R2=TRUE)
```

get fitted values
```{r}
b <- heights.mean %>% ungroup()
fit5.mean.fitted <- cbind(b, fitted(fit5.mean)) %>% as.tibble()
fit5.mean.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted <- function(fn) {
  pl <- ggplot(fn, aes(x=days)) +
  geom_line(aes(y=height), color="blue") +
  geom_line(aes(y=Estimate),color="red") +
  facet_wrap_paginate(~ID, ncol = 6, nrow = 5)
pages <- n_pages(pl)

lapply(seq_len(pages), 
       function(i) {
         ggplot(fn, aes(x=days)) +
           geom_line(aes(y=height),color="blue") +
           geom_line(aes(y=Estimate),color="red") +
           facet_wrap_paginate(~ID, ncol = 6, nrow = 5, page=i)
       }
)
}
```

```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.fitted)
```

plot fitted vs actual(modified)
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.fitted)
```

plot fitted vs actual(raw)
```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw <- function(fn) {
  
  r_squared <- summary(lm(Estimate ~ height_raw, data=fn))$adj.r.squared
  r_squared <- round(r_squared, digits=4)

  fn %>%
    mutate(days=as.factor(days)) %>%
    ggplot(aes(x=height_raw, y=Estimate, shape=days, color=days)) +
    geom_point() +
    geom_abline(intercept = 0, slope=1) +
    ggtitle(paste0("R2 = ",r_squared))

}
```

plot fitted vs actual(raw)
```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw(fit5.mean.fitted)
```

SSR on raw data set
```{r}
total_sum_of_squared_residuals_raw <- function(fn) {anova(lm(Estimate ~ height_raw, data=fn))[2,2]}
```

```{r}
SSR.fit.mean.raw <- total_sum_of_squared_residuals_raw(fit5.mean.fitted)
```

cv
```{r results='hide', message=FALSE}
SSR.fit.mean <- total_sum_of_squared_residuals(fit5.mean.fitted)
waic.fit.mean <- round(waic(fit5.mean)$waic, digits=2)
kfoldic.fit.mean <- round(kfold(fit5.mean)$kfoldic, digits=2)
```

<br>

### 3) heights.pmm

```{r, message=FALSE}
heights.pmm <- read_csv("heights.pmm.csv")
heights.pmm
```

plot
```{r results='hide', fig.keep='all'}
 lapply(1:6, function(i) {
       ggplot(aes(x=days, group=ID), data=heights.pmm) +
         geom_line(aes(y=height), color="red") +   #red: modified data
         geom_line(aes(y=height_raw), color="black") +
          facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
}
)
```

#### Try Gomertz (4-parameter) (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS

```{r}
stat.data(heights.pmm)
stat.data(heights.mean)
stat.data(heights)
```

```{r}
gompertz_4p.bf2 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

```{r results='hide'}
prior3.pmm <- c(prior(normal(170,10), nlpar="Hmax"), 
                prior(normal(15,5), nlpar="Hmin"),
                prior(normal(.5,1), nlpar="k", lb=0), 
                prior(normal(160,10),nlpar="I"),
                prior(cauchy(0,1), class="sigma"))

fit3.pmm <- brm(formula=gompertz_4p.bf2,
                data=heights.pmm,
                prior=prior3.pmm)
```

```{r}
summary(fit3.pmm, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.pmm)
pairs(fit3.pmm)
```

<br>
What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(heights.pmm$days), max(heights.pmm$days),1))
fit3.pmm.fitted <-  cbind(newdata, fitted(fit3.pmm, newdata)) %>% as.tibble() %>%
  rename(height=Estimate, lower.ci=`2.5%ile`, upper.ci=`97.5%ile`)
fit3.pmm.fitted
```

plot
```{r results='hide', fig.keep='all'}
ggplot(aes(x=days,y=height), data=heights) + 
  geom_line(aes(group=ID), alpha=.1) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.pmm.fitted)
```

<br>
**Now try adding random effects for model parameters:**
<br>

First try with only fixing Hmin

```{r}
gompertz_4p.bf3 <- bf(
  height ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))),  
  Hmax + k + I ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.pmm <- c(prior(normal(170,10), nlpar="Hmax"), 
                prior(normal(15,5), nlpar="Hmin"),
                prior(normal(.4,1), nlpar="k", lb=0), 
                prior(normal(160,10),nlpar="I"),
                prior(cauchy(0,1), class="sigma"),
                prior(cauchy(0,10), class=sd, nlpar="Hmax"),
                prior(cauchy(0,10), class=sd, nlpar="I"),
                prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.pmm <- brm(formula=gompertz_4p.bf3,
                data=heights.pmm,
                prior=prior4.pmm,
                iter=5000)
```

```{r}
summary(fit5.pmm)
```


get fitted values
```{r}
b <- heights.pmm %>% ungroup()
fit5.pmm.fitted <- cbind(b, fitted(fit5.pmm)) %>% as.tibble()
fit5.pmm.fitted
```

plot 
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.pmm.fitted)
```

plot fitted vs actual(modified)
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.pmm.fitted)
```

plot fitted vs actual(raw)
```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw(fit5.pmm.fitted)
```

```{r}
SSR.fit.pmm.raw <- total_sum_of_squared_residuals_raw(fit5.pmm.fitted)
```

cv
```{r results='hide', message=FALSE}
SSR.fit.pmm <- total_sum_of_squared_residuals(fit5.pmm.fitted)
waic.fit.pmm <- round(waic(fit5.pmm)$waic, digits=2)
kfoldic.fit.pmm <- round(kfold(fit5.pmm)$kfoldic, digits=2)
```

<br>
#### which fitted model is the better?
<br>

create an empty list for models
```{r}
#3 models: fit, fit.mean, fit.pmm

cv.list <- data.frame()
for (i in 1:3) {
  for (j in 1:4) {
    cv.list[i,j] <- 0
  }
}
colnames(cv.list) <- c("SSR(raw)","SSR","waic","kfoldic")
rownames(cv.list) <- c("fit", "fit.mean", "fit.pmm")
```

0) SSR on raw data set
```{r}
cv.list[2,1] <- SSR.fit.mean.raw
cv.list[3,1] <- SSR.fit.pmm.raw
```

1) SSR
```{r}
cv.list[1,2] <- SSR.fit
cv.list[2,2] <- SSR.fit.mean
cv.list[3,2] <- SSR.fit.pmm
```

2) CV

**WAIC(Widely Applicable Information Criterion)**
an extension of the Akaike Information Criterion (AIC) that is more fully Bayesian.

**K-fold CV**
Data are randomly partitioned into K subsets of equal size. Then the model is refit 10 times(default), each time leaving out one of the 10 subsets.

```{r}
cv.list[1,3] <- waic.fit
cv.list[2,3] <- waic.fit.mean
cv.list[3,3] <- waic.fit.pmm

cv.list[1,4] <- kfoldic.fit
cv.list[2,4] <- kfoldic.fit.mean
cv.list[3,4] <- kfoldic.fit.pmm
```

```{r}
cv.list
```

<br>
#### parameter estimates of best fitted model on phenotype height : take fit5.mean

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & I in each genotype

```{r}
height.best.fitted <- fit5.mean$fit
dimnames(height.best.fitted)
```
```{r}
height.best.fitted.summary <- summary(height.best.fitted)$summary

write.csv(height.best.fitted.summary, file = "/Users/seungmokim/414_Growth_Model/summary/growth_model_phenotypes/height/height.best.fitted.summary.csv")
``` 

r_ID__Hmax
```{r}
datalist0 = list()
for (samples in sample.list) {
  ttt0 <- paste0("r_ID__Hmax[",samples,",Intercept]")
  dat0 <- extract(height.best.fitted.summary, ttt0, permuted=TRUE)
  datalist0[[ttt0]] <- dat0
}

list.data0 = do.call(rbind, datalist0)
Hmax.ID <- data.frame(matrix(unlist(list.data0), nrow = 166, byrow = T))
row.names(Hmax.ID) <- paste0("r_ID__Hmax[",sample.list,",Intercept]")

head(Hmax.ID)

```

r_ID__Hmax
```{r}
datalist0 = list()
for (samples in sample.list) {
  ttt0 <- paste0("r_ID__Hmax[",samples,",Intercept]")
  dat0 <- extract(height.best.fitted, ttt0, permuted=TRUE)
  datalist0[[ttt0]] <- dat0
}

list.data0 = do.call(rbind, datalist0)
Hmax.ID <- data.frame(matrix(unlist(list.data0), nrow = 166, byrow = T))
row.names(Hmax.ID) <- paste0("r_ID__Hmax[",sample.list,",Intercept]")

head(Hmax.ID)
```

r_ID__k
```{r}
datalist1 = list()
for (samples in sample.list) {
  ttt1 <- paste0("r_ID__k[",samples,",Intercept]")
  dat1 <- extract(height.best.fitted, ttt1, permuted=TRUE)
  datalist1[[ttt1]] <- dat1
}

list.data1 = do.call(rbind, datalist1)
k.ID <- data.frame(matrix(unlist(list.data1), nrow = 166, byrow = T))
row.names(k.ID) <- paste0("r_ID__k[",sample.list,",Intercept]")

head(k.ID)
```

r_ID__I
```{r}
datalist2 = list()
for (samples in sample.list) {
  ttt2 <- paste0("r_ID__I[",samples,",Intercept]")
  dat2 <- extract(height.best.fitted, ttt2, permuted=TRUE)
  datalist2[[ttt2]] <- dat2
}

list.data2 = do.call(rbind, datalist2)
I.ID <- data.frame(matrix(unlist(list.data2), nrow = 166, byrow = T))
row.names(I.ID) <- paste0("r_ID__I[",sample.list,",Intercept]")

head(I.ID)
```

estimates of parameters         
```{r}
par.list = c("b_Hmax_Intercept", "b_k_Intercept", "b_I_Intercept", "b_Hmin_Intercept", "sd_ID__Hmax_Intercept",    "sd_ID__k_Intercept","sd_ID__I_Intercept","sigma", "lp__")

datalist3 = list()
for (pars in par.list) {
  dat3 <- extract(height.best.fitted, pars, permuted=TRUE)
  datalist3[[pars]] <- dat3
}

list.data3 = do.call(rbind, datalist3)
pars.est <- data.frame(matrix(unlist(list.data3), nrow = 9, byrow = T))
row.names(pars.est) <- par.list

pars.est
```

combine estimates of all parameters
```{r}
pars.estimate.height.fitted <- rbind(pars.est, Hmax.ID, k.ID, I.ID)
head(pars.estimate.height.fitted, 10)

write.csv(pars.estimate.height.fitted, file="pars.estimate.height.fitted.csv")
```

