---
title: "Brms_growth_leaf_number_Gompertz_4p"
output: html_notebook
---

Trying to fit non-linear model with BRMS(Bayesian Regression Models using Stan)
<br>
```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(magrittr)
library(ggforce)
library(gtable)
library(brms)
library(rstan)
rstan_options(auto_write = TRUE)
library(loo)
library(mice)
library(DMwR)
library(reshape2)
options(mc.cores = parallel::detectCores())
options(max.print=999999)
```

### leaf.n (raw data set)

```{r, message=FALSE}
leaf.n <- read_csv("leaf.number.csv")
leaf.n <- leaf.n %>%
  rename(leaf_n=leaf_number)
leaf.n
```

166 individuals at 4 time points
```{r message=FALSE}
ggplot(data=leaf.n, aes(x=days, y=leaf_n, group=ID)) +
    geom_line(alpha=.2, linetype="longdash") + 
    geom_point(shape=4, size=1, alpha=.1) +
    ggtitle("leaf number by days") 
```


```{r include=FALSE}
# for fixing the bug of facet_wrap_paginate()
facet_wrap_paginate <- function(facets, nrow = NULL, ncol = NULL, scales = "fixed",
                                shrink = TRUE, labeller = "label_value", as.table = TRUE,
                                switch = NULL, drop = TRUE, dir = "h", strip.position = 'top', page = 1) {
  facet <- facet_wrap(facets, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, labeller = labeller, as.table = as.table,
                      switch = switch, drop = drop, dir = dir,
                      strip.position = strip.position)
  if (is.null(nrow) || is.null(ncol)) {
    facet
  } else {
    ggproto(NULL, FacetWrapPaginate, shrink = shrink,
            params = c(facet$params, list(page = page)))
  }
}

FacetWrapPaginate <- ggproto("FacetWrapPaginate", FacetWrap,
                             setup_params = function(data, params) {
                               modifyList(
                                 params,
                                 list(
                                   max_rows = params$nrow,
                                   nrow = NULL
                                 )
                               )
                             },
                             compute_layout = function(data, params) {
                               layout <- FacetWrap$compute_layout(data, params)
                               layout$page <- ceiling(layout$ROW / params$max_rows)
                               layout
                             },
                             draw_panels = function(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params) {
                               include <- which(layout$page == params$page)
                               panels <- panels[include]
                               ranges <- ranges[include]
                               layout <- layout[include, , drop = FALSE]
                               layout$ROW <- layout$ROW - min(layout$ROW) + 1
                               x_scale_ind <- unique(layout$SCALE_X)
                               x_scales <- x_scales[x_scale_ind]
                               layout$SCALE_X <- match(layout$SCALE_X, x_scale_ind)
                               y_scale_ind <- unique(layout$SCALE_Y)
                               y_scales <- y_scales[y_scale_ind]
                               layout$SCALE_Y <- match(layout$SCALE_Y, y_scale_ind)
                               table <- FacetWrap$draw_panels(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params)
                               if (max(layout$ROW) != params$max_rows) {
                                 spacing <- theme$panel.spacing.y %||% theme$panel.spacing
                                 missing_rows <- params$max_rows - max(layout$ROW)
                                 strip_rows <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$l %in% panel_cols(table)$l])
                                 strip_rows <- strip_rows[as.numeric(table$heights[strip_rows]) != 0]
                                 axis_b_rows <- unique(table$layout$t[grepl('axis-b', table$layout$name)])
                                 axis_b_rows <- axis_b_rows[as.numeric(table$heights[axis_b_rows]) != 0]
                                 axis_t_rows <- unique(table$layout$t[grepl('axis-t', table$layout$name)])
                                 axis_t_rows <- axis_t_rows[as.numeric(table$heights[axis_t_rows]) != 0]
                                 table <- gtable_add_rows(table, unit(missing_rows, 'null'))
                                 table <- gtable_add_rows(table, spacing * missing_rows)
                                 if (length(strip_rows) != 0) {
                                   table <- gtable_add_rows(table, min(table$heights[strip_rows]) * missing_rows)
                                 }
                                 if (params$free$x) {
                                   if (length(axis_b_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_b_rows]) * missing_rows)
                                   }
                                   if (length(axis_t_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_t_rows]) * missing_rows)
                                   }
                                 }
                               }
                               if (max(layout$COL) != params$ncol) {
                                 spacing <- theme$panel.spacing.x %||% theme$panel.spacing
                                 missing_cols <- params$ncol - max(layout$COL)
                                 strip_cols <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$t %in% panel_rows(table)$t])
                                 strip_cols <- strip_cols[as.numeric(table$widths[strip_cols]) != 0]
                                 axis_l_cols <- unique(table$layout$l[grepl('axis-l', table$layout$name)])
                                 axis_l_cols <- axis_l_cols[as.numeric(table$widths[axis_l_cols]) != 0]
                                 axis_r_cols <- unique(table$layout$l[grepl('axis-r', table$layout$name)])
                                 axis_r_cols <- axis_r_cols[as.numeric(table$widths[axis_r_cols]) != 0]
                                 table <- gtable_add_cols(table, unit(missing_cols, 'null'))
                                 table <- gtable_add_cols(table, spacing * missing_cols)
                                 if (length(strip_cols) != 0) {
                                   table <- gtable_add_cols(table, min(table$widths[strip_cols]) * missing_cols)
                                 }
                                 if (params$free$y) {
                                   if (length(axis_l_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_l_cols]) * missing_cols)
                                   }
                                   if (length(axis_r_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_r_cols]) * missing_cols)
                                   }
                                 }
                               }
                               table
                             }
)

n_pages <- function(plot) {
  page <- ggplot_build(plot)$layout$panel_layout$page
  if (!is.null(page)) {
    max(page)
  } else {
    NULL
  }
}
```

<br>
**Try Gompertz (4-parameter) Model (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS**
<br>

First set up the formula
```{r}
gompertz_4p.bf1 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-k*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```


    Hmax, asymptotic height at which growth is zero
    Hmin, lower asymptotic height
    k, growth rate
    I, time at the inflection point

```{r}
stat.data <- function(data) {
  data %>% 
  group_by(days) %>%
  summarize(meadian=median(leaf_n),
            max=max(leaf_n),
            min=min(leaf_n),
            sd=sd(leaf_n))
}
```

```{r}
stat.data(leaf.n)
```

Priors.  Hmin and Hmax use median at start and end dates.

```{r results='hide'}
prior1 <- c(prior(normal(18,5), nlpar="Hmax"), 
            prior(normal(8,4), nlpar="Hmin"),
            prior(normal(-1,1), nlpar="k"), 
            prior(normal(130,10), nlpar="I"))

fit1 <- brm(formula=gompertz_4p.bf1,
            data=leaf.n,
            prior=prior1)
```

```{r}
summary(fit1, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit1)
pairs(fit1)
```
<br>
```{r}
gompertz_4p.bf2 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/10)*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #paramters do not vary for individuals
  nl=TRUE)
```

 
```{r results='hide'}
prior2 <- c(prior(normal(18,5), nlpar="Hmax"), 
            prior(normal(8,4), nlpar="Hmin"),
            prior(normal(-1,1), nlpar="k", ub=0), 
            prior(normal(150,10), nlpar="I"))

fit2 <- brm(formula=gompertz_4p.bf2,
            data=leaf.n,
            prior=prior2)
```

```{r}
summary(fit2, waic=TRUE, R2=TRUE)
```


```{r results='hide', fig.keep='all'} 
plot(fit2)
pairs(fit2)
```

<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(leaf.n$days), max(leaf.n$days),1))
fit2.fitted <-  cbind(newdata, fitted(fit2, newdata)) %>% as.tibble() %>%
  rename(leaf_n=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'} 
ggplot(aes(x=days, y=leaf_n),data=NULL) + 
  geom_line(aes(group=ID), alpha=.1, data=leaf.n) + 
  geom_line(color="skyblue", lwd=1.5, data=fit2.fitted)
```

<br>

**Now try adding random effects for model parameters:**
<br>

First try with only fixing Hmin

```{r}
gompertz_4p.bf3 <- bf(
   leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/10)*(days - I))),  
   Hmax + I + k  ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE) 
```

```{r results='hide'}
prior4 <- c(prior(normal(18,5), nlpar="Hmax"), 
            prior(normal(8,4), nlpar="Hmin"),
            prior(normal(-2,1), nlpar="k", ub=0), 
            prior(normal(150,10), nlpar="I"),
            prior(cauchy(0,1), class=sigma),
            prior(cauchy(0,5), class=sd, nlpar="Hmax"),
            prior(cauchy(0,10), class=sd, nlpar="I"),
            prior(cauchy(0,1), class=sd, nlpar="k"))

fit5 <- brm(formula=gompertz_4p.bf3,
            data=leaf.n,
            prior=prior4,
            iter=5000)
```

```{r}
summary(fit5, waic=TRUE, R2=TRUE)
```

```{r}
#plot(fit5)
```


<br>

get fitted values
```{r}
b <- leaf.n %>% ungroup()
fit5.fitted <- cbind(b, fitted(fit5)) %>% as.tibble()
fit5.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted <- function(fn) {
 pl <- ggplot(fn, aes(x=days)) +
  geom_line(aes(y=leaf_n), color="blue") +
  geom_line(aes(y=Estimate),color="red") +
  facet_wrap_paginate(~ID, ncol = 6, nrow = 5)
pages <- n_pages(pl)

lapply(seq_len(pages), 
       function(i) {
         ggplot(fn, aes(x=days)) +
           geom_line(aes(y=leaf_n),color="blue") +
           geom_line(aes(y=Estimate),color="red") +
           facet_wrap_paginate(~ID, ncol = 6, nrow = 5, page=i)
       }
  )
}
```


```{r}
plot.fitted(fit5.fitted)
```

plot fitted vs actual:
```{r}
plot.fitted.actual <- function(fn) {
r_squared <- summary(lm(Estimate ~ leaf_n, data=fn))$adj.r.squared
r_squared <- round(r_squared, digits = 4)

fn %>%
  mutate(days=as.factor(days)) %>%
  ggplot(aes(x=leaf_n, y=Estimate, shape=days, color=days)) +
  geom_point() +
  geom_abline(intercept = 0, slope=1) +
  ggtitle(paste0("R2 = ",r_squared))
}
```

```{r}
plot.fitted.actual(fit5.fitted)
```

SSR on raw data set
```{r}
total_sum_of_squared_residuals <- function(fn) {anova(lm(Estimate ~ leaf_n, data=fn))[2,2]}
```

cv
```{r}
SSR.fit <- total_sum_of_squared_residuals(fit5.fitted)
waic.fit <- round(waic(fit5)$waic, digits=2)
#kfoldic.fit <- round(kfold(fit5)$kfoldic, digits=2)
```


### leaf.n.mean
abnormal looking value : replced by the average between the previous and the next value
the increasing value since the minimum value : replaced with the minimum values

```{r, message=FALSE}
leaf.n.mean <- read_csv("leaf.number.mean.csv")
leaf.n.mean <- leaf.n.mean %>% select(ID, date, days, leaf_n=leaf_number, leaf_n_raw=leaf_number_raw)
leaf.n.mean
```


```{r results='hide', fig.keep='all'}
 lapply(1:6, function(i) {
       ggplot(aes(x=days, group=ID), data=leaf.n.mean) +
         geom_line(aes(y=leaf_n), color="red") +   #red: modified data
         geom_line(aes(y=leaf_n_raw), color="black") +
          facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
}
)
```

<br>
#### Try gompertz (4-parameter) (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS 
<br>

```{r}
stat.data(leaf.n.mean)
stat.data(leaf.n)
```

```{r}
gompertz_4p.bf1 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))), 
  Hmax + Hmin + k + I ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

```{r results='hide'}
prior3.mean <- c(prior(normal(20,5), nlpar="Hmax"), 
                 prior(normal(6,4), nlpar="Hmin"),
                 prior(normal(-5,1), nlpar="k", ub=0), 
                 prior(normal(150,10), nlpar="I"))

fit3.mean <- brm(formula=gompertz_4p.bf1,
                 data=leaf.n,
                 prior=prior3.mean)
```


```{r}
summary(fit3.mean, waic=TRUE, R2=TRUE)
```


```{r results='hide', fig.keep='all'}
plot(fit3.mean)
pairs(fit3.mean)
```


What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(leaf.n.mean$days), max(leaf.n.mean$days),1))
fit3.mean.fitted <-  cbind(newdata, fitted(fit3.mean, newdata)) %>% as.tibble() %>%
  rename(leaf_n=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
fit3.mean.fitted
```

plot
```{r}
leaf.n.mean.curve <- ggplot(aes(x=days, y=leaf_n),data=NULL) +
  geom_line(aes(group=ID), alpha=.1, data=leaf.n) + 
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.fitted) +
  ggtitle("fitted curve using leaf_number.mean")

ggsave(filename="leaf.n.mean.curve.pdf", plot=leaf.n.mean.curve, 
       width = 7, height = 5)
```

```{r}
gompertz_4p.fn <- function(Hmax,  Hmin,k, I, days) {
  Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I)))
}

for(I1 in seq(120,160,10)) {
  for(k1 in seq(-5,0,.5)) {
  tmp.leaf.number <- gompertz_4p.fn(Hmax=20,
                                    Hmin=6,
                                    k=k1,
                                    I=I1,
                                    days=newdata$days)
   abc <- data.frame(newdata$days, tmp.leaf.number)
   p <- ggplot(data=abc, aes(newdata$days, tmp.leaf.number)) +
     geom_line() + ylim(0,30) + ggtitle(paste0("I=",I1," k=",k1))
   print(p)
  }
}
```


First try with only fixing Hmin
```{r}
gompertz_4p.bf3 <- bf(
   leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))),  
   Hmax + k + I ~ (1|ID), # vary for individuals
   Hmin ~ 1, # do not vary per individual
   nl=TRUE) 
```

```{r}
prior4.mean <- c(prior(normal(20,5), nlpar="Hmax"), 
                 prior(normal(6,4), nlpar="Hmin"),
                 prior(normal(-5,1), nlpar="k", ub=0), 
                 prior(normal(150,10), nlpar="I"),
                 prior(cauchy(0,1), class=sigma),
                 prior(cauchy(0,5), class=sd, nlpar="Hmax"),
                 prior(cauchy(0,10), class=sd, nlpar="I"),
                 prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean <- brm(formula=gompertz_4p.bf3,
                 data=leaf.n.mean,
                 prior=prior4.mean,
                 iter=5000)
```


```{r}
summary(fit5.mean, waic=TRUE, R2=TRUE)
```


```{r}
#plot(fit5.mean)
```

<br>

get fitted values
```{r}
b <- leaf.n.mean %>% ungroup()
fit5.mean.fitted <- cbind(b, fitted(fit5.mean)) %>% as.tibble()
fit5.mean.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.fitted)
```

plot fitted vs actual(modified):
```{r}
(
leaf.n.mean.R2curve <- plot.fitted.actual(fit5.mean.fitted) +
  xlab("observed (leaf_number.mean)") + ylab("predicted")
)

ggsave(filename="leaf.n.mean.R2curve.pdf", plot=leaf.n.mean.R2curve, 
       width = 7, height = 5)
```

plot fitted vs actual(raw):
```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw <- function(fn) {
  
  r_squared <- summary(lm(Estimate ~ leaf_n_raw, data=fn))$adj.r.squared
  r_squared <- round(r_squared, digits=4)

  fn %>%
    mutate(days=as.factor(days)) %>%
    ggplot(aes(x=leaf_n_raw, y=Estimate, shape=days, color=days)) +
    geom_point() +
    geom_abline(intercept = 0, slope=1) +
    ggtitle(paste0("R2 = ",r_squared)) +
    xlab("observed (leaf_number)")

}
```


```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw(fit5.mean.fitted)
```

SSR on raw data set
```{r}
total_sum_of_squared_residuals_raw <- function(fn) {anova(lm(Estimate ~ leaf_n_raw, data=fn))[2,2]}

SSR.fit.mean.raw <- total_sum_of_squared_residuals_raw(fit5.mean.fitted)
```

cv
```{r}
SSR.fit.mean <- total_sum_of_squared_residuals(fit5.mean.fitted)
waic.fit.mean <- round(waic(fit5.mean)$waic, digits=2)
#kfoldic.fit.mean <- round(kfold(fit5.mean)$kfoldic, digits=2)
```

<br>



<br>

#### which fitted model is the better?

<br>

create an empty list for models
```{r results='hide'}
#2 models: fit, fit.mean

cv.list <- data.frame()
for (i in 1:2) {
  for (j in 1:4) {
    cv.list[i,j] <- 0
  }
}
colnames(cv.list) <- c("SSR(raw)","SSR","waic","kfoldic")
rownames(cv.list) <- c("fit", "fit.mean")
```

0) SSR on raw data set
```{r}
cv.list[2,1] <- SSR.fit.mean.raw
```

1) SSR
```{r}
cv.list[1,2] <- SSR.fit
cv.list[2,2] <- SSR.fit.mean
```

2) CV

**WAIC(Widely Applicable Information Criterion)**
an extension of the Akaike Information Criterion (AIC) that is more fully Bayesian.

**K-fold CV**
Data are randomly partitioned into K subsets of equal size. Then the model is refit 10 times(default), each time leaving out one of the 10 subsets.


```{r}
cv.list[1,3] <- waic.fit
cv.list[2,3] <- waic.fit.mean

#cv.list[1,4] <- kfoldic.fit
#cv.list[2,4] <- kfoldic.fit.mean
```

```{r}
cv.list
```

<br>

#### parameter estimates of best fitted model on phenotype height : take fit5.mean

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & I in each genotype

```{r}
leaf.n.best.fitted <- fit5.mean$fit
dimnames(leaf.n.best.fitted)
```

```{r}
leaf.n.best.fitted.summary <- summary(leaf.n.best.fitted)$summary

write.csv(leaf.n.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/leaf_number/leaf.n.best.fitted.summary.csv")
``` 

### leaf.n.mean.added (individual)

Da-Ae, Da-Ol1 and F1 data added individually
(e.g. Da-Ae_1, Da-Ae_2)

```{r, message=FALSE}
leaf.n.mean.added <- read_csv("leaf.number.mean.added.csv")
leaf.n.mean.added
```

<br>

Try Gompertz with 4-parameter (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS 

<br>


```{r}
stat.data(leaf.n.mean.added)
stat.data(leaf.n.mean)
```



```{r}
gompertz_4p.bf2 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100) * (days - I))),
  Hmax + Hmin + k + I ~ 1, 
  nl=TRUE)
```

```{r results='hide'}
prior3.mean.added <- c(prior(normal(19,5), nlpar="Hmax"), 
                       prior(normal(6.5,4), nlpar="Hmin"),
                       prior(normal(-5,1), nlpar="k", ub=0), 
                       prior(normal(150,10), nlpar="I"))

fit3.mean.added <- brm(formula=gompertz_4p.bf2,
                       data=leaf.n.mean.added,
                       prior=prior3.mean.added)
```

```{r}
summary(fit3.mean.added, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added)
pairs(fit3.mean.added)
```

<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(leaf.n.mean.added$days), max(leaf.n.mean.added$days),1))
fit3.mean.added.fitted <-  cbind(newdata, fitted(fit3.mean.added, newdata)) %>% as.tibble() %>%
  rename(leaf_n=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r}
ggplot(aes(x=days, y=leaf_n),data=NULL) +
  geom_line(aes(group=ID), alpha=.1, data=leaf.n) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.fitted)
```


```{r}
gompertz_4p.bf3 <- bf(
   leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)*(days - I))),  
   Hmax + k + I ~ (1|ID), # vary for individuals
   Hmin ~ 1, # do not vary per individual
   nl=TRUE) 
```


```{r results='hide'}
prior4.mean.added <- c(prior(normal(19,5), nlpar="Hmax"), 
                       prior(normal(6.5,4), nlpar="Hmin"),
                       prior(normal(-5,1), nlpar="k", ub=0), 
                       prior(normal(150,10), nlpar="I"),
                       prior(cauchy(0,1), class=sigma),
                       prior(cauchy(0,5), class=sd, nlpar="Hmax"),
                       prior(cauchy(0,10), class=sd, nlpar="I"),
                       prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added <- brm(formula=gompertz_4p.bf3,
                       data=leaf.n.mean.added,
                       prior=prior4.mean.added,
                       iter = 5000)
```

```{r}
summary(fit5.mean.added, waic=TRUE, R2=TRUE)
```


```{r}
#plot(fit5.mean.added)
```

get fitted values
```{r}
b <- leaf.n.mean.added %>% ungroup()
fit5.mean.added.fitted <- cbind(b, fitted(fit5.mean.added)) %>% as.tibble()
fit5.mean.added.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.fitted)
```

plot fitted vs actual(modified)
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.fitted)
```

#### parameter estimates of best fitted model on phenotype lobe number : take fit5.mean.added

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & I of each genotype

```{r}
leaf.n.added.best.fitted <- fit5.mean.added$fit
dimnames(leaf.n.added.best.fitted)
```

```{r}
leaf.n.added.best.fitted.summary <- summary(leaf.n.added.best.fitted)$summary

write.csv(leaf.n.added.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/leaf_number/leaf.n.added(individual).best.fitted.summary.csv")
``` 

<br>

### leaf.n.mean.added (identical)

Da-Ae, Da-Ol1 and F1 data added (e.g. Da-Ae_1 --> Da-Ae, Da-Ae_2 --> Da-Ae)

```{r, message=FALSE}
leaf.n.mean.added.ident <- read_csv("leaf.number.mean.added.ident.csv")
leaf.n.mean.added.ident
```

<br>

Try Gompertz with 4-parameter (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS 

<br>

```{r}
stat.data(leaf.n.mean.added.ident)
stat.data(leaf.n.mean)
```

```{r}
gompertz_4p.bf2 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100)* (days - I))),
  Hmax + Hmin + k + I ~ 1, 
  nl=TRUE)
```

```{r results='hide'}
prior3.mean.added.ident <- c(prior(normal(19,5), nlpar="Hmax"), 
                             prior(normal(6.5,4), nlpar="Hmin"),
                             prior(normal(-5,1), nlpar="k", ub=0), 
                             prior(normal(150,10), nlpar="I"))

fit3.mean.added.ident <- brm(formula=gompertz_4p.bf2,
                             data=leaf.n.mean.added.ident,
                             prior=prior3.mean.added.ident)
```

```{r}
summary(fit3.mean.added.ident, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added.ident)
pairs(fit3.mean.added.ident)
```

<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(leaf.n.mean.added.ident$days), max(leaf.n.mean.added.ident$days),1))
fit3.mean.added.ident.fitted <-  cbind(newdata, fitted(fit3.mean.added.ident, newdata)) %>% as.tibble() %>%
  rename(leaf_n=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
fit3.mean.added.ident.fitted
```

plot
```{r}
ggplot(aes(x=days, y=leaf_n),data=NULL) +
  geom_line(aes(group=ID), alpha=.1, data=leaf.n) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.ident.fitted)
```


```{r}
gompertz_4p.bf3 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100) * (days - I))),
  Hmax + k + I ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean.added.ident <- c(prior(normal(19,5), nlpar="Hmax"), 
                       prior(normal(6.5,4), nlpar="Hmin"),
                       prior(normal(-5,1), nlpar="k", ub=0), 
                       prior(normal(150,10), nlpar="I"),
                       prior(cauchy(0,1), class=sigma),
                       prior(cauchy(0,5), class=sd, nlpar="Hmax"),
                       prior(cauchy(0,10), class=sd, nlpar="I"),
                       prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added.ident <- brm(formula=gompertz_4p.bf3,
                             data=leaf.n.mean.added.ident,
                             prior=prior4.mean.added.ident,
                             iter = 5000)
```

```{r}
summary(fit5.mean.added.ident, waic=TRUE, R2=TRUE)
```


```{r}
#plot(fit5.mean.added.ident)
```

get fitted values
```{r}
b <- leaf.n.mean.added.ident %>% ungroup()
fit5.mean.added.ident.fitted <- cbind(b, fitted(fit5.mean.added.ident)) %>% as.tibble()
fit5.mean.added.ident.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.ident.fitted)
```

plot fitted vs actual(modified)
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.ident.fitted)
```

#### parameter estimates of best fitted model on phenotype lobe number : take fit5.mean.added.ident

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & I of each genotype

```{r}
leaf.n.added.ident.best.fitted <- fit5.mean.added.ident$fit
dimnames(leaf.n.added.ident.best.fitted)
```

```{r}
leaf.n.added.ident.best.fitted.summary <- summary(leaf.n.added.ident.best.fitted)$summary

write.csv(leaf.n.added.ident.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/leaf_number/leaf.n.added(identical).best.fitted.summary.csv")
``` 

<br>

### leaf.n.mean.added(mean)

taking mean values of replicates

```{r, message=FALSE}
leaf.n.mean.added.mean <- read_csv("leaf.number.mean.added(mean).csv")
leaf.n.mean.added.mean
```

<br>

Try Gompertz with 4-parameter (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.html) by using BRMS 

<br>

```{r}
stat.data(leaf.n.mean.added.mean)
stat.data(leaf.n.mean)
```



```{r}
gompertz_4p.bf2 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100) * (days - I))),
  Hmax + Hmin + k + I ~ 1, 
  nl=TRUE)
```

```{r results='hide'}
prior3.mean.added.mean<- c(prior(normal(20,5), nlpar="Hmax"), 
                           prior(normal(6,4), nlpar="Hmin"),
                           prior(normal(-5,1), nlpar="k", ub=0), 
                           prior(normal(150,10), nlpar="I"))

fit3.mean.added.mean <- brm(formula=gompertz_4p.bf2,
                             data=leaf.n.mean.added.mean,
                             prior=prior3.mean.added.mean)
```

```{r}
summary(fit3.mean.added.mean, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added.mean)
pairs(fit3.mean.added.mean)
```

<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(leaf.n.mean.added.mean$days), max(leaf.n.mean.added.mean$days),1))
fit3.mean.added.mean.fitted <-  cbind(newdata, fitted(fit3.mean.added.mean, newdata)) %>% as.tibble() %>%
  rename(leaf_n=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r}
ggplot(aes(x=days, y=leaf_n),data=NULL) +
  geom_line(aes(group=ID), alpha=.1, data=leaf.n) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.mean.fitted)
```


```{r}
gompertz_4p.bf3 <- bf(
  leaf_n ~ Hmin + (Hmax - Hmin) * exp(-exp(-(k/100) * (days - I))),
  Hmax + k + I ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean.added.mean <- c(prior(normal(20,5), nlpar="Hmax"), 
                       prior(normal(6,4), nlpar="Hmin"),
                       prior(normal(-5,1), nlpar="k", ub=0), 
                       prior(normal(150,10), nlpar="I"),
                       prior(cauchy(0,1), class=sigma),
                       prior(cauchy(0,5), class=sd, nlpar="Hmax"),
                       prior(cauchy(0,10), class=sd, nlpar="I"),
                       prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added.mean <- brm(formula=gompertz_4p.bf3,
                             data=leaf.n.mean.added.mean,
                             prior=prior4.mean.added.mean,
                             iter = 5000)
```

```{r}
summary(fit5.mean.added.mean, waic=TRUE, R2=TRUE)
```


```{r}
#plot(fit5.mean.added.mean)
```

get fitted values
```{r}
b <- leaf.n.mean.added.mean %>% ungroup()
fit5.mean.added.mean.fitted <- cbind(b, fitted(fit5.mean.added.mean)) %>% as.tibble()
fit5.mean.added.mean.fitted
```

plot
```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.mean.fitted)
```

plot fitted vs actual(modified)
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.mean.fitted)
```

#### parameter estimates of best fitted model on phenotype leaf number : take fit5.mean.added.mean

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & I of each genotype

```{r}
leaf.n.added.mean.best.fitted <- fit5.mean.added.mean$fit
dimnames(leaf.n.added.mean.best.fitted)
```

```{r}
leaf.n.added.mean.best.fitted.summary <- summary(leaf.n.added.mean.best.fitted)$summary

write.csv(leaf.n.added.mean.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/leaf_number/leaf.n.added(mean).best.fitted.summary.csv")
``` 









