---
title: "Brms_growth_width_Weibull"
output: html_notebook
---

<br>

**Go to the end of this file for the parameter estimates of the best fitted model on phenotype width**
<br>

Trying to fit non-linear model with BRMS(Bayesian Regression Models using Stan)
<br>

```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(magrittr)
library(ggforce)
library(gtable)
library(brms)
library(loo)
library(mice)
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
options(max.print=999999)
library(reshape2)
library(DMwR)
```

```{r message=FALSE}
widths <- read_csv("widths.csv")
widths

sample.list <- unique(widths$ID)
```


```{r results='hide', fig.keep='all'}
ggplot(data=widths, aes(x=days, y=width, group=ID)) +
    geom_line(alpha=.1) + 
    geom_point(size=.1, alpha=.05) +
    ggtitle("width by days")
```

```{r include=FALSE}
# for fixing the bug of facet_wrap_paginate()
facet_wrap_paginate <- function(facets, nrow = NULL, ncol = NULL, scales = "fixed",
                                shrink = TRUE, labeller = "label_value", as.table = TRUE,
                                switch = NULL, drop = TRUE, dir = "h", strip.position = 'top', page = 1) {
  facet <- facet_wrap(facets, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, labeller = labeller, as.table = as.table,
                      switch = switch, drop = drop, dir = dir,
                      strip.position = strip.position)
  if (is.null(nrow) || is.null(ncol)) {
    facet
  } else {
    ggproto(NULL, FacetWrapPaginate, shrink = shrink,
            params = c(facet$params, list(page = page)))
  }
}

FacetWrapPaginate <- ggproto("FacetWrapPaginate", FacetWrap,
                             setup_params = function(data, params) {
                               modifyList(
                                 params,
                                 list(
                                   max_rows = params$nrow,
                                   nrow = NULL
                                 )
                               )
                             },
                             compute_layout = function(data, params) {
                               layout <- FacetWrap$compute_layout(data, params)
                               layout$page <- ceiling(layout$ROW / params$max_rows)
                               layout
                             },
                             draw_panels = function(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params) {
                               include <- which(layout$page == params$page)
                               panels <- panels[include]
                               ranges <- ranges[include]
                               layout <- layout[include, , drop = FALSE]
                               layout$ROW <- layout$ROW - min(layout$ROW) + 1
                               x_scale_ind <- unique(layout$SCALE_X)
                               x_scales <- x_scales[x_scale_ind]
                               layout$SCALE_X <- match(layout$SCALE_X, x_scale_ind)
                               y_scale_ind <- unique(layout$SCALE_Y)
                               y_scales <- y_scales[y_scale_ind]
                               layout$SCALE_Y <- match(layout$SCALE_Y, y_scale_ind)
                               table <- FacetWrap$draw_panels(panels, layout, x_scales, y_scales, ranges, coord, data, theme, params)
                               if (max(layout$ROW) != params$max_rows) {
                                 spacing <- theme$panel.spacing.y %||% theme$panel.spacing
                                 missing_rows <- params$max_rows - max(layout$ROW)
                                 strip_rows <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$l %in% panel_cols(table)$l])
                                 strip_rows <- strip_rows[as.numeric(table$heights[strip_rows]) != 0]
                                 axis_b_rows <- unique(table$layout$t[grepl('axis-b', table$layout$name)])
                                 axis_b_rows <- axis_b_rows[as.numeric(table$heights[axis_b_rows]) != 0]
                                 axis_t_rows <- unique(table$layout$t[grepl('axis-t', table$layout$name)])
                                 axis_t_rows <- axis_t_rows[as.numeric(table$heights[axis_t_rows]) != 0]
                                 table <- gtable_add_rows(table, unit(missing_rows, 'null'))
                                 table <- gtable_add_rows(table, spacing * missing_rows)
                                 if (length(strip_rows) != 0) {
                                   table <- gtable_add_rows(table, min(table$heights[strip_rows]) * missing_rows)
                                 }
                                 if (params$free$x) {
                                   if (length(axis_b_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_b_rows]) * missing_rows)
                                   }
                                   if (length(axis_t_rows) != 0) {
                                     table <- gtable_add_rows(table, min(table$heights[axis_t_rows]) * missing_rows)
                                   }
                                 }
                               }
                               if (max(layout$COL) != params$ncol) {
                                 spacing <- theme$panel.spacing.x %||% theme$panel.spacing
                                 missing_cols <- params$ncol - max(layout$COL)
                                 strip_cols <- unique(table$layout$t[grepl('strip', table$layout$name) & table$layout$t %in% panel_rows(table)$t])
                                 strip_cols <- strip_cols[as.numeric(table$widths[strip_cols]) != 0]
                                 axis_l_cols <- unique(table$layout$l[grepl('axis-l', table$layout$name)])
                                 axis_l_cols <- axis_l_cols[as.numeric(table$widths[axis_l_cols]) != 0]
                                 axis_r_cols <- unique(table$layout$l[grepl('axis-r', table$layout$name)])
                                 axis_r_cols <- axis_r_cols[as.numeric(table$widths[axis_r_cols]) != 0]
                                 table <- gtable_add_cols(table, unit(missing_cols, 'null'))
                                 table <- gtable_add_cols(table, spacing * missing_cols)
                                 if (length(strip_cols) != 0) {
                                   table <- gtable_add_cols(table, min(table$widths[strip_cols]) * missing_cols)
                                 }
                                 if (params$free$y) {
                                   if (length(axis_l_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_l_cols]) * missing_cols)
                                   }
                                   if (length(axis_r_cols) != 0) {
                                     table <- gtable_add_cols(table, min(table$widths[axis_r_cols]) * missing_cols)
                                   }
                                 }
                               }
                               table
                             }
)

n_pages <- function(plot) {
  page <- ggplot_build(plot)$layout$panel_layout$page
  if (!is.null(page)) {
    max(page)
  } else {
    NULL
  }
}
```


```{r results='hide', fig.keep='all'}
lapply(1:6, function(i) {
    ggplot(widths) +
      geom_line(aes(x=days, y=width, group=ID)) +
      facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
    }
)
```
<br>

#### Try weibull (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.htm ) 
<br><br>

First set up the formula
```{r}
weibull.bf1 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-(k*days)^delta), #Weibull model
  Hmax + Hmin + k + delta ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

Priors.  Hmin and Hmax use median at start and end dates.
```{r}
stat.data <- function(data) {
  data %>% 
  group_by(days) %>%
  summarize(meadian=median(width),
            max=max(width),
            min=min(width),
            sd=sd(width))
}
```

```{r}
stat.data(widths)
```

```{r results='hide'}
prior1 <- c(prior(normal(42,10), nlpar="Hmin"),
            prior(normal(62,7), nlpar="Hmax"),
            prior(normal(1,1), nlpar="k"),
            prior(normal(2,1), nlpar="delta"))

fit1 <- brm(formula=weibull.bf1,
            data=widths,
            prior=prior1)
```

```{r}
summary(fit1, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit1)
pairs(fit1)
```

So with these priors it seems that the model can flip between having high and low Hmin and Hmax.  This relates to the delta parameter flipping signs.  So one possibility is to keep delta positive.  Or more tightly constrain the priors on Hmax and Hmin.

```{r results='hide'}
prior2 <- c(prior(normal(42,10), nlpar="Hmin"),
            prior(normal(62,7),nlpar="Hmax"),
            prior(normal(1,1),nlpar="k"),
            prior(normal(2,1),nlpar="delta", lb=0))

fit2 <- brm(formula=weibull.bf1,
            data=widths,
            prior=prior2)
```

```{r}
summary(fit2, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit2)
pairs(fit2)
```

<br>
rescale k to get it more reasonable
<br>

```{r}
weibull.bf2 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + Hmin + k + delta ~ 1, #general model, paramters do not vary for individuals
  nl=TRUE)
```

```{r results='hide'}
prior3 <- c(prior(normal(20,10), nlpar="Hmin"),
            prior(normal(60,7), nlpar="Hmax"),
            prior(normal(.9,1), nlpar="k"),
            prior(normal(4,1), nlpar="delta", lb=0))

fit3 <- brm(formula=weibull.bf2,
            data=widths,
            prior=prior3)
```

```{r}
summary(fit3, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3)
pairs(fit3)
```

<br>
What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(widths$days), max(widths$days),1))
fit3.fitted <-  cbind(newdata, fitted(fit3, newdata)) %>% as.tibble() %>%
  rename(width=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'}
pl <- ggplot(aes(x=days, y=width),data=NULL)
pl <- pl + geom_line(aes(group=ID), alpha=.2, data=widths)
pl + geom_line(color="skyblue", lwd=1.5, data=fit3.fitted)
```

<br>
Now try adding random effects for model parameters:
<br>

What parameters do we think might be interesting to allow to vary?  Probably not Hmin.  Try making a series of plots to see how varying delta or k affects things:

```{r}
weibull.fn <- function(Hmax,Hmin,k,delta,days) {
    Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta) #Weibull model
}

for(delta1 in seq(3,5,.25)) {
  tmp.widths <- weibull.fn(Hmax=62,
                           Hmin=20,
                           k=.7,
                           delta=delta1,
                           days=newdata$days)
  abc <- data.frame(newdata$days, tmp.widths)
  p <- ggplot(data=abc, aes(newdata$days, tmp.widths)) +
    geom_line() + ylim(0,100) + ggtitle("delta=",delta1)
  print(p)
}
```

```{r}
for(k1 in seq(.5,1.5,.1)) {
  tmp.widths <- weibull.fn(Hmax=60,
                           Hmin=20,
                           k=k1,
                           delta=4,
                           days=newdata$days)
  abc <- data.frame(newdata$days, tmp.widths)
  p <- ggplot(data=abc, aes(newdata$days, tmp.widths)) +
    geom_line() + ylim(0,80) + ggtitle("k=",k1)
  print(p)
}
```

<br>
First try with only fixing Hmin
```{r}
weibull.bf3 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + k + delta ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```

```{r results='hide'}
prior4 <- c(prior(normal(42,10), nlpar="Hmin"),
            prior(normal(62,7), nlpar="Hmax"),
            prior(normal(1,1), nlpar="k"),
            prior(normal(8,.5), nlpar="delta", lb=0),
            prior(cauchy(0,1), class=sigma),
            prior(cauchy(0,7), class=sd, nlpar="Hmax"),
            prior(cauchy(0,.5), class=sd, nlpar="delta"),
            prior(cauchy(0,1), class=sd, nlpar="k"))

fit5 <- brm(formula = weibull.bf3,
            data=widths,
            prior=prior4,
            iter=5000)
```

```{r}
summary(fit5, waic=TRUE, R2=TRUE)
```

<br>

get fitted values
```{r}
b <- widths %>% ungroup()
fit5.fitted <- cbind(b, fitted(fit5)) %>% as.tibble()
fit5.fitted
```

plot

```{r results='hide', fig.keep='all'}
plot.fitted <- function(fitted.data) {
   pl <- ggplot(fitted.data, aes(x=days)) +
     geom_line(aes(y=width),color="blue") +
     geom_line(aes(y=Estimate),color="red") +
     facet_wrap_paginate(~ID, ncol = 6, nrow = 5)
   pages <- n_pages(pl)

   lapply(seq_len(pages), 
          function(i) {
            ggplot(fitted.data, aes(x=days)) +
              geom_line(aes(y=width), color="blue") +
              geom_line(aes(y=Estimate), color="red") +
              facet_wrap_paginate(~ID, ncol = 6, nrow = 5, page=i)
          }
    )
}

plot.fitted(fit5.fitted)
```

plot fitted vs actual:
```{r}
plot.fitted.actual <- function(fn) {
  
  r_squared <- summary(lm(Estimate ~ width, data=fn))$adj.r.squared
  r_squared <- round(r_squared, digits=4)

  fn %>%
    mutate(days=as.factor(days)) %>%
    ggplot(aes(x=width, y=Estimate, shape=days, color=days)) +
    geom_point() +
    geom_abline(intercept = 0, slope=1) +
    ggtitle(paste0("R2 = ",r_squared))

}
```

```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.fitted)
```

```{r}
total_sum_of_squared_residuals <- function(fn) {anova(lm(Estimate ~ width, data=fn))[2,2]}
```

cv
```{r message=FALSE}
TSSR.fit <- total_sum_of_squared_residuals(fit5.fitted)
waic.fit <- round(waic(fit5)$waic, digits=2)
#kfoldic.fit <- round(kfold(fit5)$kfoldic, digits=2)
```

<br>

### widths.mean

```{r, message=FALSE}
widths.mean <- read_csv("widths.mean.csv")
widths.mean
```

```{r results='hide', fig.keep='all'}
lapply(1:6, function(i) {
       ggplot(aes(x=days, group=ID), data=widths.mean) +
         geom_line(aes(y=width), color="red") +
         geom_line(aes(y=width_raw), color="black") +
          facet_wrap_paginate(~ID, ncol = 6, nrow = 5,  page =i)
}
)
```

#### Try weibull (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.htm ) 
<br>

```{r}
stat.data(widths.mean) 
stat.data(widths) 
```

```{r results='hide'}
weibull.bf2 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta),
  Hmax + Hmin + k + delta ~ 1, #paramters do not vary for individuals
  nl=TRUE)

prior3.mean <- c(prior(normal(40,10), nlpar="Hmin"),
                 prior(normal(65,7), nlpar="Hmax"),
                 prior(normal(1,1), nlpar="k"),
                 prior(normal(4,1), nlpar="delta", lb=0))

fit3.mean <- brm(formula=weibull.bf2,
                 data=widths.mean,
                 prior=prior3.mean)
```

```{r}
summary(fit3.mean, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean)
pairs(fit3.mean)
```


<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(widths.mean$days), max(widths.mean$days),1))
fit3.mean.fitted <-  cbind(newdata, fitted(fit3.mean, newdata)) %>%
  as.tibble() %>%
  rename(width=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'}
(
width.mean.curve <- ggplot(aes(x=days, y=width),data=NULL) +
  geom_line(aes(group=ID), linetype="longdash", alpha=.1, data=widths.mean) +
  geom_line(color="skyblue", lwd=1.5, data=fit3.mean.fitted) +
  ggtitle("fitted curve using width.mean")
)
   
ggsave(filename="width.mean.curve.pdf", plot=width.mean.curve, 
       width = 7, height = 5)
```
<br>

**Now try adding random effects for model parameters:**
<br>

What parameters do we think might be interesting to allow to vary?  Probably not Hmin.  Try making a series of plots to see how varying delta or k affects things:

```{r}
weibull.fn <- function(Hmax,Hmin,k,delta,days) {
    Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta) #Weibull model
}

for(delta1 in seq(3,8,.5)) {
  tmp.widths <- weibull.fn(Hmax=65,
                            Hmin=40,
                            k=1,
                            delta=delta1,
                            days=newdata$days)
   abc <- data.frame(newdata$days, tmp.widths)
  p <- ggplot(data=abc, aes(newdata$days, tmp.widths)) +
    geom_line() + ylim(0,80) + ggtitle("delta=",delta1)
  print(p)
}
```

```{r}
for(k1 in seq(0,5,.5)) {
  tmp.width <- weibull.fn(Hmax=65,
                            Hmin=40,
                            k=k1,
                            delta=5,
                            days=newdata$days)
  abc <- data.frame(newdata$days, tmp.widths)
  p <- ggplot(data=abc, aes(newdata$days, tmp.widths)) +
    geom_line() + ylim(0,80) + ggtitle("k=",k1)
  print(p)
}
```
<br>

try with only fixing Hmin

```{r}
weibull.bf3 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + k + delta ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean <- c(prior(normal(40,10), nlpar="Hmin"),
                 prior(normal(65,7), nlpar="Hmax"),
                 prior(normal(1,1), nlpar="k"),
                 prior(normal(8,.5), nlpar="delta", lb=0),
                 prior(cauchy(0,1), class=sigma),
                 prior(cauchy(0,7), class=sd, nlpar="Hmax"),
                 prior(cauchy(0,.5), class=sd, nlpar="delta"),
                 prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean <- brm(formula=weibull.bf3,
                 data=widths.mean,
                 prior=prior4.mean,
                 iter=5000)
```

```{r}
summary(fit5.mean, waic=TRUE, R2=TRUE)
```

```{r}
#plot(fit5.mean)
```
<br>

get fitted values
```{r}
b <- widths.mean %>% ungroup()
fit5.mean.fitted <- cbind(b, fitted(fit5.mean)) %>% as.tibble()
fit5.mean.fitted
```

plot

```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.fitted)
```

plot fitted vs actual(modified):
```{r results='hide', fig.keep='all'}
(
width.mean.R2curve <- plot.fitted.actual(fit5.mean.fitted) +
  xlab("observed (width.mean)") + ylab("predicted")
)

ggsave(filename="width.mean.R2curve.pdf", plot=width.mean.R2curve, 
       width = 7, height = 5)
```

plot fitted vs actual(raw):
```{r}
plot.fitted.actual.raw <- function(fn) {
  
  r_squared <- summary(lm(Estimate ~ width_raw, data=fn))$adj.r.squared
  r_squared <- round(r_squared, digits=4)

  fn %>%
    mutate(days=as.factor(days)) %>%
    ggplot(aes(x=width_raw, y=Estimate, shape=days, color=days)) +
    geom_point() +
    geom_abline(intercept = 0, slope=1) +
    ggtitle(paste0("R2 = ",r_squared)) +
    xlab("observed (width)") + ylab("predicted")

}
```

```{r results='hide', fig.keep='all'}
plot.fitted.actual.raw(fit5.mean.fitted)
```

TSSR on raw data set
```{r}
total_sum_of_squared_residuals_raw <- function(fn) {anova(lm(Estimate ~ width_raw, data=fn))[2,2]}

TSSR.fit.mean.raw <- total_sum_of_squared_residuals_raw(fit5.mean.fitted)
```

cv
```{r message=FALSE}
TSSR.fit.mean <- total_sum_of_squared_residuals(fit5.mean.fitted)
waic.fit.mean <- round(waic(fit5.mean)$waic, digits=2)
#kfoldic.fit.mean <- round(kfold(fit5.mean)$kfoldic, digits=2)
```


<br>
#### which fitted model is the better?
<br>

create an empty list for models
```{r results='hide'}
#2 models: fit, fit.mean

cv.list <- data.frame()
for (i in 1:2) {
  for (j in 1:4) {
    cv.list[i, j] <- 0
  }
}
colnames(cv.list) <- c("SSR(raw)", "SSR","WAIC", "KFOLDIC")
rownames(cv.list) <- c("fit", "fit.mean")
```

0) TSSR on raw data set
```{r}
cv.list[2,1] <- TSSR.fit.mean.raw
```

1) TSSR
```{r}
cv.list[1,2] <- TSSR.fit
cv.list[2,2] <- TSSR.fit.mean
```

2) CV

**WAIC(Widely Applicable Information Criterion)**
an extension of the Akaike Information Criterion (AIC) that is more fully Bayesian.

**K-fold CV**
Data are randomly partitioned into K subsets of equal size. Then the model is refit 10 times(default), each time leaving out one of the 10 subsets.


```{r}
cv.list[1,3] <- waic.fit
cv.list[2,3] <- waic.fit.mean
```

```{r}
#cv.list[1,4] <- kfoldic.fit
#cv.list[2,4] <- kfoldic.fit.mean
```

```{r}
cv.list
```

<br>
#### parameter estimates of best fitted model on phenotype width : take fit5.mean
<br>

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & delta of each genotype

```{r}
width.best.fitted <- fit5.mean$fit
dimnames(width.best.fitted)
```

```{r}
width.best.fitted.summary <- summary(width.best.fitted)$summary

write.csv(width.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/width/width.best.fitted.summary.csv")
``` 


### widths.mean.added(individual)

Da-Ae, Da-Ol1 and F1 data added individually
(e.g. Da-Ae_1, Da-Ae_2)

```{r, message=FALSE}
widths.mean.added <- read_csv("widths.mean.added(individual).csv")
widths.mean.added
```


Try weibull (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.htm ) 
<br>

```{r}
stat.data(widths.mean.added)
stat.data(widths.mean) 
```

```{r results='hide'}
weibull.bf2 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta),
  Hmax + Hmin + k + delta ~ 1, #paramters do not vary for individuals
  nl=TRUE)

prior3.mean.added <- c(prior(normal(40,10), nlpar="Hmin"),
                 prior(normal(65,7), nlpar="Hmax"),
                 prior(normal(1,1), nlpar="k"),
                 prior(normal(4,1), nlpar="delta", lb=0))

fit3.mean.added <- brm(formula=weibull.bf2,
                 data=widths.mean.added,
                 prior=prior3.mean.added)
```

```{r}
summary(fit3.mean.added, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added)
pairs(fit3.mean.added)
```


<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(widths.mean.added$days), max(widths.mean.added$days),1))
fit3.mean.added.fitted <-  cbind(newdata, fitted(fit3.mean.added, newdata)) %>%
  as.tibble() %>%
  rename(width=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'}
pl <- ggplot(aes(x=days, y=width),data=NULL)
pl <- pl + geom_line(aes(group=ID), alpha=.1, data=widths.mean.added)
pl + geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.fitted) +
  ggtitle("width.mean vs. days")
```
<br>

**Now try adding random effects for model parameters:**
<br>


<br>

try with only fixing Hmin

```{r}
weibull.bf3 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + k + delta ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean.added <- c(prior(normal(40,10), nlpar="Hmin"),
                 prior(normal(65,7), nlpar="Hmax"),
                 prior(normal(1,1), nlpar="k"),
                 prior(normal(8,.5), nlpar="delta", lb=0),
                 prior(cauchy(0,1), class=sigma),
                 prior(cauchy(0,7), class=sd, nlpar="Hmax"),
                 prior(cauchy(0,.5), class=sd, nlpar="delta"),
                 prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added <- brm(formula=weibull.bf3,
                 data=widths.mean.added,
                 prior=prior4.mean.added,
                 iter=5000)
```

```{r}
summary(fit5.mean.added, waic=TRUE, R2=TRUE)
```

```{r}
#plot(fit5.mean.added)
```
<br>

get fitted values
```{r}
b <- widths.mean.added %>% ungroup()
fit5.mean.added.fitted <- cbind(b, fitted(fit5.mean.added)) %>% as.tibble()
fit5.mean.added.fitted
```

plot

```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.fitted)
```

plot fitted vs actual(modified):
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.fitted)
```

<br>
#### parameter estimates of best fitted model on phenotype width : take fit5.mean.added
<br>

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & delta of each genotype

```{r}
width.added.best.fitted <- fit5.mean.added$fit
dimnames(width.added.best.fitted)
```

```{r}
width.added.best.fitted.summary <- summary(width.added.best.fitted)$summary

write.csv(width.added.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/width/width.added(individual).best.fitted.summary.csv")
``` 

<br>

### widths.mean.added(identical)

Da-Ae, Da-Ol1 and F1 data added (e.g. Da-Ae_1 --> Da-Ae, Da-Ae_2 --> Da-Ae)

```{r, message=FALSE}
widths.mean.added.ident <- read_csv("widths.mean.added(identical).csv")
widths.mean.added.ident
```


Try weibull (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.htm ) 
<br>

```{r}
stat.data(widths.mean.added.ident)
stat.data(widths.mean.added)
stat.data(widths.mean) 
```

```{r results='hide'}
weibull.bf2 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta),
  Hmax + Hmin + k + delta ~ 1, #paramters do not vary for individuals
  nl=TRUE)

prior3.mean.added.ident <- c(prior(normal(40,10), nlpar="Hmin"),
                             prior(normal(65,7), nlpar="Hmax"),
                             prior(normal(1,1), nlpar="k"),
                             prior(normal(4,1), nlpar="delta", lb=0))

fit3.mean.added.ident <- brm(formula=weibull.bf2,
                             data=widths.mean.added.ident,
                             prior=prior3.mean.added.ident)
```

```{r}
summary(fit3.mean.added.ident, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added.ident)
pairs(fit3.mean.added.ident)
```


<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(widths.mean.added.ident$days), max(widths.mean.added.ident$days),1))
fit3.mean.added.ident.fitted <-  cbind(newdata, fitted(fit3.mean.added.ident, newdata)) %>%
  as.tibble() %>%
  rename(width=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'}
pl <- ggplot(aes(x=days, y=width),data=NULL)
pl <- pl + geom_line(aes(group=ID), alpha=.1, data=widths.mean.added.ident)
pl + geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.ident.fitted) +
  ggtitle("width.mean vs. days")
```
<br>

**Now try adding random effects for model parameters:**
<br>


<br>

try with only fixing Hmin

```{r}
weibull.bf3 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + k + delta ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean.added.ident <- c(prior(normal(40,10), nlpar="Hmin"),
                             prior(normal(65,7), nlpar="Hmax"),
                             prior(normal(1,1), nlpar="k"),
                             prior(normal(8,.5), nlpar="delta", lb=0),
                             prior(cauchy(0,1), class=sigma),
                             prior(cauchy(0,7), class=sd, nlpar="Hmax"),
                             prior(cauchy(0,.5), class=sd, nlpar="delta"),
                             prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added.ident <- brm(formula=weibull.bf3,
                             data=widths.mean.added.ident,
                             prior=prior4.mean.added.ident,
                             iter=5000)
```

```{r}
summary(fit5.mean.added.ident, waic=TRUE, R2=TRUE)
```

```{r}
#plot(fit5.mean.added.ident)
```
<br>

get fitted values
```{r}
b <- widths.mean.added.ident %>% ungroup()
fit5.mean.added.ident.fitted <- cbind(b, fitted(fit5.mean.added.ident)) %>% as.tibble()
fit5.mean.added.ident.fitted
```

plot

```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.ident.fitted)
```

plot fitted vs actual(modified):
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.ident.fitted)
```

<br>
#### parameter estimates of best fitted model on phenotype width : take fit5.mean.added.ident
<br>

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & delta of each genotype

```{r}
width.added.ident.best.fitted <- fit5.mean.added.ident$fit
dimnames(width.added.ident.best.fitted)
```

```{r}
width.added.ident.best.fitted.summary <- summary(width.added.ident.best.fitted)$summary

write.csv(width.added.ident.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/width/width.added(individual).best.fitted.summary.csv")
``` 

<br>

### widths.mean.added(mean)

taking mean values of replicates

```{r, message=FALSE}
widths.mean.added.mean <- read_csv("widths.mean.added(mean).csv")
widths.mean.added.mean
```


Try weibull (see http://www.pisces-conservation.com/growthhelp/index.html?weibul.htm ) 
<br>

```{r}
stat.data(widths.mean.added.mean)
stat.data(widths.mean) 
```

```{r results='hide'}
weibull.bf2 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta),
  Hmax + Hmin + k + delta ~ 1, #paramters do not vary for individuals
  nl=TRUE)

prior3.mean.added.mean <- c(prior(normal(40,10), nlpar="Hmin"),
                             prior(normal(65,7), nlpar="Hmax"),
                             prior(normal(1,1), nlpar="k"),
                             prior(normal(4,1), nlpar="delta", lb=0))

fit3.mean.added.mean <- brm(formula=weibull.bf2,
                             data=widths.mean.added.mean,
                             prior=prior3.mean.added.mean)
```

```{r}
summary(fit3.mean.added.mean, waic=TRUE, R2=TRUE)
```

```{r results='hide', fig.keep='all'}
plot(fit3.mean.added.mean)
pairs(fit3.mean.added.mean)
```


<br>

What does the fit look like?

```{r}
newdata <- data.frame(days=seq(min(widths.mean.added.mean$days), max(widths.mean.added.mean$days),1))
fit3.mean.added.mean.fitted <-  cbind(newdata, fitted(fit3.mean.added.mean, newdata)) %>%
  as.tibble() %>%
  rename(width=Estimate, lower.ci='2.5%ile', upper.ci='97.5%ile')
```

plot
```{r results='hide', fig.keep='all'}
pl <- ggplot(aes(x=days, y=width),data=NULL)
pl <- pl + geom_line(aes(group=ID), alpha=.1, data=widths.mean.added.mean)
pl + geom_line(color="skyblue", lwd=1.5, data=fit3.mean.added.mean.fitted) +
  ggtitle("width.mean vs. days")
```
<br>

**Now try adding random effects for model parameters:**
<br>

try with only fixing Hmin

```{r}
weibull.bf3 <- bf(
  width ~ Hmax - (Hmax - Hmin) * exp(-((k/100)*days)^delta), #Weibull model
  Hmax + k + delta ~ (1|ID), # vary for individuals
  Hmin ~ 1, # do not vary per individual
  nl=TRUE)
```


```{r results='hide'}
prior4.mean.added.mean <- c(prior(normal(40,10), nlpar="Hmin"),
                             prior(normal(65,7), nlpar="Hmax"),
                             prior(normal(1,1), nlpar="k"),
                             prior(normal(8,.5), nlpar="delta", lb=0),
                             prior(cauchy(0,1), class=sigma),
                             prior(cauchy(0,7), class=sd, nlpar="Hmax"),
                             prior(cauchy(0,.5), class=sd, nlpar="delta"),
                             prior(cauchy(0,1), class=sd, nlpar="k"))

fit5.mean.added.mean <- brm(formula=weibull.bf3,
                             data=widths.mean.added.mean,
                             prior=prior4.mean.added.mean,
                             iter=5000)
```

```{r}
summary(fit5.mean.added.mean, waic=TRUE, R2=TRUE)
```

```{r}
#plot(fit5.mean.added.mean)
```
<br>

get fitted values
```{r}
b <- widths.mean.added.mean %>% ungroup()
fit5.mean.added.mean.fitted <- cbind(b, fitted(fit5.mean.added.mean)) %>% as.tibble()
fit5.mean.added.mean.fitted
```

plot

```{r results='hide', fig.keep='all'}
plot.fitted(fit5.mean.added.mean.fitted)
```

plot fitted vs actual(modified):
```{r results='hide', fig.keep='all'}
plot.fitted.actual(fit5.mean.added.mean.fitted)
```

<br>
#### parameter estimates of best fitted model on phenotype width : take fit5.mean.added.mean
<br>

    read 
    1) population (fixed) & group level (random) effects
    2) parameters: Hmax, k & delta of each genotype

```{r}
width.added.mean.best.fitted <- fit5.mean.added.mean$fit
dimnames(width.added.mean.best.fitted)
```

```{r}
width.added.mean.best.fitted.summary <- summary(width.added.mean.best.fitted)$summary

write.csv(width.added.mean.best.fitted.summary, file = "/Users/seungmokim/Desktop/414_growth_model/width/width.added(mean).best.fitted.summary.csv")
``` 




